SDR enhancement by clouds

### 2024-04-02 article/article.Rmd
Commit 2024-04-02 11:11

@@

Some of the proposed underling mechanisms of those events have been summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds, and the
observer.  As such, there multiple contributing mechanism can create the
observed irradiance enhancements.

@@

Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.
@Gueymard2017; @Veerman2022

>>>>

Some of the proposed underling mechanisms of those events have been summarized by
@Gueymard2017, and include scattering on the edge of cumulus clouds or through thin
cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness, constitution and type, and the relative position of the sun, the clouds,
and the observer [@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanism that can create
the observed irradiance enhancements.

<!--
Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.  @Gueymard2017; @Veerman2022
-->

@@

@@
